Topic and tone of political news articles in German online media.

### 2018-04-06 paper/docs/04_Modelresults_50.Rmd
add new ccf

ggsave(filename = "../figs/sentscore_monthly.png", plot = p1,  width = 9,
       height = 6)
```

@@

p1 <- ggplot(p, 
       aes(reorder(topic_name, topic), 
           sentiment_w, 
           group = site,
           label = obs)) +
  geom_col(fill=col[3], alpha = 0.8) +
  #geom_line(color = col[2], size = 0.8) +
  geom_text(size = 2) +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="Sentiment Score (weighted)",
       title = "",
       subtitle = "Numbers indicate the ") +
  theme(axis.text.y = element_text(size =8),
        axis.text.x = element_text(size=4, angle = 90),
        axis.title.x = element_text(size = 5))

ggsave(filename = "../figs/sentscore_site.png", plot = p1, width = 9,
       height = 5)
```

@@

```{r}
plot_ccf <- function(corr1, corr2, ...){

  # Create empty matrix
  corr <- expand.grid(names(corr1), names(corr2))
  corr$correlation <- NA

@@

  for (corr1Id in 1:ncol(corr2)) {
    c1 = corr2[,corr1Id]
    #print(names(corr2[,corr1Id]))

    for(corr2Id in 1:ncol(corr1)) {
      c2 = corr1[,corr2Id]
      #print(names(corr1[,corr2Id]))
      correlation = ccf(c1, c2, lag.max = 0,
                      na.action = na.contiguous, plot=F)
      corr[x,3] <- correlation$acf[1]

@@

      ### Plot Corr ##
      ggplot(corr, aes(Var2, Var1,
                 fill = correlation,
                 label = round(correlation,2))) +
        geom_tile(color="white", ...) +
        geom_text(size = 3.5, color = col[5]) +
        viridis::scale_fill_viridis(limits=c(-1, 1)) +
        labs(x="", y="", fill="",
             title = "",
             ...)
}
```

##### 3.1.1. Overall
```{r fig.height=6, fig.width=8}
group1 %>%
  select(yearmonth, topic_name, sentiment_n) %>%
  spread(topic_name, sentiment_n) %>%
  select(- yearmonth) -> corr1

polls_monthly %>% select(- yearmonth) -> corr2

p <- plot_ccf(corr1, corr2, alpha = 0.8,
              subtitle = "Election polls vs. topic sentiment value (monthly)")

@@

>>>>

ggsave(filename = "../figs/sentscore_monthly.png", plot = p1, 
       height = 6)
```

@@

p1 <- ggplot(p, 
       aes(reorder(topic_name, topic), 
           sentiment_w, 
           group = site,
           label = obs)) +
  geom_col(fill=col[3], alpha = 0.8) +
  #geom_line(color = col[2], size = 0.8) +
  #geom_text(size = 2) +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="Sentiment Score (weighted)",
       title = "") +
  theme(axis.text.y = element_text(size =8),
        axis.text.x = element_text(size=4, angle = 90),
        axis.title.x = element_text(size = 5))

ggsave(filename = "../figs/sentscore_site.png", plot = p1, 
       height = 5)
```

@@

##### 3.1.1. Overall
```{r}
group1 %>%
  select(yearmonth, topic_name, sentiment_n) %>%
  spread(topic_name, sentiment_n) %>%
  select(- yearmonth) -> corr1

polls_monthly %>% select(- yearmonth) -> corr2
```

```{r}
# Create empty matrix
corr <- expand.grid(names(corr1), names(corr2))

corr$`-3` <- NA
corr$`-2` <- NA
corr$`-1` <- NA
corr$`0` <- NA
corr$`1` <- NA
corr$`2` <- NA
corr$`3` <- NA

@@

for (corr1Id in 1:ncol(corr2)) {
  c1 = corr2[,corr1Id]

  for(corr2Id in 1:ncol(corr1)) {
    c2 = corr1[,corr2Id]
    correlation = ccf(c1, c2, lag.max = 3,
                      na.action = na.contiguous, plot=F)

    corr[x,"-3"] <- correlation$acf[1]
    corr[x,"-2"] <- correlation$acf[2]
    corr[x,"-1"] <- correlation$acf[3]
    corr[x,"0"] <- correlation$acf[4]
    corr[x,"1"] <- correlation$acf[5]
    corr[x,"2"] <- correlation$acf[6]
    corr[x,"3"] <- correlation$acf[7]

@@

corr <- corr %>%
  gather(lag, correlation, `-3`:`3`) %>%
  mutate(lag = as.numeric(lag))
```

```{r fig.height=6, fig.width=8}
p <- corr %>%
  filter(lag == 0) %>%
  ggplot(aes(Var2, Var1,
                 fill = correlation,
                 label = round(correlation,2))) +
        geom_tile(color="white", alpha=0.8) +
        geom_text(size = 3.5) +
        #viridis::scale_fill_viridis(limits=c(-1, 1)) +
        labs(x="", y="", fill="",
             title = "",
             subtitle = "Election polls vs. topic sentiment value (monthly)")

@@

The variance of the cross-correlation coefficient under the null hypothesis of zero correlation is approx $1/n$ where $n$ is the length of the series. The coefficients are also asymptotically normal. So approximate critical values (at the 5% level) are $±2/\sqrt{n}$.

```{r}
critical_val <- 2/sqrt(nrow(corr1))
```

```{r}
# insert linebreak for long strings
linebreak <- function(s) {
  gsub('(.{1,12})(\\s|$)', '\\1\n', s)
}
```

```{r fig.height=7, fig.width=14}
p <- ggplot(corr, aes(lag, correlation,
                 #fill = Var1,
                 group=Var2)) +
  geom_col(fill = col[3]) +
  scale_x_continuous(breaks = c(-3:3)) +
  labs(x="Lag",y="Cross Correlation") +
  geom_hline(yintercept = critical_val, linetype = 2, color = col[5]) +
  geom_hline(yintercept = -(critical_val), linetype = 2, color = col[5]) +
  facet_grid(Var2~Var1, labeller=labeller(Var1 = linebreak)) +
  theme(strip.text = element_text(size=12),
        strip.text.y = element_text(size=12),
        axis.text = element_text(size = 10),
        axis.title = element_text(size=12))

ggsave(filename = "../figs/ccf2.png", plot = p,
       width = 16,
       height = 10,
       dpi = 600)
```

### 2018-04-06 paper/writing/structure.tex
add tables for regression results
add new ccf

We will select the following topics from the whole set. The most frequent words of these topics at each news website can be seen in Appendix \ref{apx_tf}:

@@

Next, the differences of topic prevalence for given document characteristics can be estimated \citep{roberts_model_2016}. For each topic $k$ a linear model is estimated, where the documents $d$ are observations, the dependent variable is the posterior probability of that topic ($\theta_{d}$) and the covariates are dummy variables that are 1 if the document was published by the respective website and 0 otherwise (see equation \ref{eq_1}). As the dependent variable is a vector containing proportions that sum up to 1, the QR decomposition of the model is computed prior to the estimation of the coefficients. To incorporate uncertainty in the dependent variable, a set of topic proportions are drawn from the variational posterior (the unnormalized topic proportions) repeated times. Then, the coefficients are computed as the average over all results \citep{roberts_stm:_2016}.

@@

Figure \ref{fig_estimateEffects} shows the regression results for the above selected topics. The coefficients indicate the deviation from the base value of Bild.de. Starting from above it becomes apparent that the topic prevalence of topic 46 (regarding the CDU) is significantly less for Tagesschau.de and Stern.de. The other media do not show any significant difference to Bild.de for this topic. The opposite is true for topic 37: With the exception of Stern.de and DIE WELT, topic prevalence for this topic is significantly higher for all media than for Bild.de. With the following two topics on AfD it is striking that the topic prevalence at Tagesschau.de is significantly lower compared to Bild.de. The topics concerning the Jamaican coalition (topic 27) and the failure (topic 26) seem to be discussed most likely at Bild.de. The case is different for the CSU issue (Topic 23), where SPIEGEL ONLINE has the highest probability. The same applies to the topic related to the personnel debates of the SPD (22). However, Bild.de has the highest topic prevalence for the topic related to votes within the SPD, especially the vote on the grand coalition. The same applies to the topic regarding the SPD in general and Martin Schulz in particular (1). Overall, topics concerning the SPD seem to be more frequent at Bild.de than in the other media. Moreover, the distribution of topics at FOCUS ONLINE seems to be the most similar to that of Bild.de, while the biggest differences exist between Bild.de and Tagesschau.de.

@@

The following figure shows the results of the analysis for each topic on a monthly basis, aggregated on all newspaper. Each sentiment value is weighted by the relative share of the topic in the overall reporting of that month.

@@

If aggregated by news provider, some differences between the sites are discernible (Figure \ref{fig_sentscore_site}\footnote{The numbers reflect the number of observations.}). To begin with, it can be noted that on average all topics are discussed negatively by all news providers, except topic 22, which mainly covers the personnel debates of the SPD and has a positive value at Tagesschau.de. One striking feature is the way in which the Jamaica negotiations and their failure are reported (topics 27 and 26). Although all providers discuss this topics in a negative light, Bild.de reports them particularly negative. The same applies to the reports on the grand coalition, where the value of ZEIT ONLINE is the most negative.

We use two different Figures to analyze the differences between the media outlets graphically: We use the bar plot to examine the polarity tendencies of the individual topics within a medium (\ref{fig_sentscore_site}) and the radar plot to observe the differences between the media (\ref{fig_sentscore_radar}).

@@

\begin{figure}[H]
	\caption{Sentiment Score by news wire}
	\begin{center}
			\includegraphics[width=\textwidth,keepaspectratio]{../figs/sentscore_site.png}
			\label{fig_sentscore_site}
	\end{center}
\end{figure}

A good overview of how differently the topics are discussed by the providers is shown in Figure \ref{fig_sentscore_radar}. It gets evident that the sentiment value of the media differs most notably with regard to topic 27 and topic 4, i. e. the topics on which the coalition negotiations are reported. With regard to the Jamaica coalition, Bild.de reports the most and tagesschau.de the least negative. The reporting of ZEIT ONLINE concerning the grand coalition is the one with the most negative sentiment value and again Tagesschau.de, together with stern.de, the one with the value which is least negative. Furthermore, it becomes evident that the negative sentiment value of FOCUS ONLINE regarding topic 17 is high in relation to the other media. FOCUS ONLINE thus reports comparatively more negatively on the debates within the SPD. This includes in particular the vote on a possible coalition with CDU/CSU. For topic 1, which also deals with the SPD, the value of FOCUS ONLINE is rather negative, only undercut by Bild.de. Topics related to AfD do not show striking differences.

@@

After the above figures have been analyzed, the following points can be summarized: (a) The sentiment value of the SPD is decreasing over time, especially in regard to internal votes. (b) The topics relating to the coalition talks on Jamaica (26, 27) and the grand coalition (4) are discussed rather critically, but they also show the greatest differences within the media. In contrast, the tonality of the topics in relation to the AfD shows rather small differences. (c) Overall, the sentiment value at Tagesschau.de is the least negative and only shows a comparatively strong negative value at topic 23, concerning the CSU.

@@

This section seeks to examine the temporal association between sentiment reflected in online news content and phone survey poll results in Germany. Specifically, it aims to find the extent to which online sentiment and phone survey results correlate. I use the data from the "Sonntagsumfrage" (Sunday survey) from infratest dimap\footnote{https://www.infratest-dimap.de/umfragen-analysen/bundesweit/sonntagsfrage/}. The institution regularly asks at least 1000 German citizens the question: "Which party would you choose if federal elections take place next Sunday?" The survey thus measures the current election tendencies and therefore reflects an intermediate state in the opinion-forming process of the electoral population.

@@

\begin{figure}[H]
	\caption{Cross-Correlation at lag 0}
	\begin{center}
			\includegraphics[width=\textwidth,keepaspectratio]{../figs/ccf.png}
			\label{fig_ccf}
	\end{center}
\end{figure}
% Anders darstellen. 
% Eventuell auch Lags zeigen.

@@

\section*{Appendix}

\subsection{Most frequent words}\label{apx_tf}
% 1, 2
\begin{figure}[H]
	\begin{center}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/plotquote1.png}
		\end{subfigure}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/plotquote2.png}
		\end{subfigure}
	\end{center}
\end{figure}

@@

>>>>

The remaining analysis is limited to topics closely related to one or more parties. For this reason, the following topics were selected. The most frequent words of these topics at each news website can be seen in Appendix \ref{apx_tf}:

@@

To estimate the differences of topic prevalence of the mentioned topics for the different websites, a linear model is calculated for each topic $k$, where the documents $D$ are observations, the dependent variable is the posterior probability of the respective topic ($\theta_{d}$) and the covariates are dummy variables that are 1 if the document was published by the respective website and 0 otherwise (see equation \ref{eq_1}). As the dependent variable is a vector containing proportions that sum up to 1, the QR decomposition of the model is computed prior to the estimation of the coefficients. To incorporate uncertainty in the dependent variable, a set of topic proportions are drawn from the variational posterior (the unnormalized topic proportions) repeated times. Then, the coefficients are computed as the average over all results \citep{roberts_model_2016}.

@@

Figure \ref{fig_estimateEffects} shows the regression results for the above selected topics (See Appendix \ref{apx_coeff} for the result tables). The coefficients indicate the deviation from the base value of Bild.de. Starting from above it becomes apparent that the topic prevalence of topic 46 (regarding the CDU) is significantly less for Tagesschau.de and Stern.de. The other media do not show any significant difference to Bild.de for this topic. The opposite is true for topic 37: With the exception of Stern.de and DIE WELT, topic prevalence for this topic is significantly higher for all media than for Bild.de. With the following two topics on AfD it is striking that the topic prevalence at Tagesschau.de is significantly lower compared to Bild.de. The topics concerning the Jamaican coalition (topic 27) and the failure (topic 26) seem to be discussed most likely at Bild.de. The case is different for the CSU issue (Topic 23), where SPIEGEL ONLINE has the highest probability. The same applies to the topic related to the personnel debates of the SPD (22). However, Bild.de has the highest topic prevalence for the topic related to votes within the SPD, especially the vote on the grand coalition. The same applies to the topic regarding the SPD in general and Martin Schulz in particular (1). Overall, topics concerning the SPD seem to be more frequent at Bild.de than in the other media. Moreover, the distribution of topics at FOCUS ONLINE seems to be the most similar to that of Bild.de, while the biggest differences exist between Bild.de and Tagesschau.de.

@@

The following figure shows the results of the analysis for each topic on a monthly basis, aggregated on all newspapers. Each sentiment value is weighted by the relative share of the topic in the overall reporting of that month.

@@

If aggregated by news provider, some differences between the sites are discernible (Figure \ref{fig_sentscore_site}). To begin with, it can be noted that on average all topics are discussed negatively by all news providers, except topic 22, which mainly covers the personnel debates of the SPD and has a positive value at Tagesschau.de. One striking feature is the way in which the Jamaica negotiations and their failure are reported (topics 27 and 26). Although all providers discuss this topics in a negative light, Bild.de reports them particularly negative. The same applies to the reports on the grand coalition, where the value of ZEIT ONLINE is the most negative.

We use two different Figures to analyze the differences between the media outlets graphically: We use the bar plot to examine the polarity tendencies of the individual topics within a medium (Figure \ref{fig_sentscore_site}) and the radar plot to observe the differences between the media (Figure \ref{fig_sentscore_radar}).

@@

\begin{figure}[H]
	\caption{Sentiment Score by news website}
	\begin{center}
			\includegraphics[width=\textwidth,keepaspectratio]{../figs/sentscore_site.png}
			\label{fig_sentscore_site}
	\end{center}
\end{figure}

A good overview of how differently the topics are discussed by the providers is shown in Figure \ref{fig_sentscore_radar}. It becomes evident that the sentiment value of the media differs most notably with regard to topic 27 and topic 4, i. e. the topics on which the coalition negotiations are reported. With regard to the Jamaica coalition, Bild.de reports the most and tagesschau.de the least negative. The reporting of ZEIT ONLINE concerning the grand coalition is the one with the most negative sentiment value and again Tagesschau.de, together with stern.de, the one with the value which is least negative. Furthermore, it becomes evident that the negative sentiment value of FOCUS ONLINE regarding topic 17 is high in relation to the other media. FOCUS ONLINE thus reports comparatively more negatively on the debates within the SPD. This includes in particular the vote on a possible coalition with CDU/CSU. For topic 1, which also deals with the SPD, the value of FOCUS ONLINE is rather negative, only undercut by Bild.de. Topics related to AfD do not show striking differences.

@@

After the above figures have been analyzed, the following points can be summarized:

\begin{enumerate}
	\item The sentiment value of the SPD is decreasing over time, especially in regard to internal votes. 
	\item The topics relating to the coalition talks on Jamaica (26, 27) and the grand coalition (4) are discussed rather critically, but they also show the greatest differences within the media. In contrast, the tonality of the topics in relation to the AfD shows rather small differences. 
	\item Overall, the sentiment value at Tagesschau.de is the least negative and only shows a comparatively strong negative value at topic 23, concerning the CSU.
\end{enumerate}

@@

This section seeks to examine the temporal association between sentiment reflected in online news content and phone survey poll results in Germany. Specifically, it aims to find the extent to which online sentiment and phone survey results correlate. I use the data from the "Sonntagsumfrage" (Sunday survey) from infratest dimap.\footnote{https://www.infratest-dimap.de/umfragen-analysen/bundesweit/sonntagsfrage/} The institution regularly asks at least 1000 German citizens the question: "Which party would you choose if federal elections take place next Sunday?" The survey thus measures the current election tendencies and therefore reflects an intermediate state in the opinion-forming process of the electoral population.

@@

\begin{figure}[H]
	\caption{Cross-Correlation}
	\begin{center}
			\includegraphics[width=\textwidth,keepaspectratio]{../figs/ccf2.png}
			\label{fig_ccf}
	\end{center}
\end{figure}
% Anders darstellen. 
% Eventuell auch Lags zeigen.

@@

\printbibliography
\section*{Appendix}

\subsection*{Most frequent words\label{apx_tf}
% 1, 2
\begin{figure}[H]
	\begin{center}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/plotquote1.png}
		\end{subfigure}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/plotquote2.png}
		\end{subfigure}
	\end{center}
\end{figure}

@@

\subsection*{Regression Results}\label{apx_coeff}

\input{tables/coeff1}
\input{tables/coeff2}
\input{tables/coeff3}
\input{tables/coeff4}
\input{tables/coeff5}
